ProbabilityBoundsAnalysis.jl:\\ an arithmetic of probabilities and sets of probabilities

### 2021-09-30 paper/paper.tex
adds some final revisions

\section{Probability Boxes}
\label{sec:pboxes}

>>>>

\iffalse
\subsection{Automatic uncertainty in a programming language: why Julia?}

The long term goal of probability bounds analysis is to create a fully uncertain programming language, where any computer variable may be represented as an interval, distribution, p-box or other imprecise quantity. Such a framework would allow for uncertain extensions of deterministic functions to be computed in an automatic, rigorous and tight fashion. Those with little knowledge of probability theory can add uncertainty to their computations with minimal effort. Stochastic calculations often require many years of training to implement and interpret correctly, and are usually not rigorous and are famously computationally expensive. \texttt{ProbabilityBoundsAnalysis.jl} provides the type structure for distribution functions and p-boxes which is rigorous, and has many of the base operations required for an uncertain programming language, which are rigorous and computationally effient. In this section we argue why Julia is an ideal target language for such an uncertainty language.

\subsubsection{Multiple dispatch} \hfill \break

Multiple dispatch allows Julia packages with completely different functionalities to work together with minimal effort. One of the great successes of \texttt{IntervalArithmetic.jl} is that it allows for intervals to be propagated through nearly any Julia function, including those from different packages.

\subsubsection{Parametric typing} \hfill \break

Parametric typing allows one to create very generic data types, parametrised on other types. This is

For example, an uncertain

an interval of type Int64 (\texttt(Interval{Int64})) can be made and destiguised of t

\subsubsection{Metaprogramming} \hfill \break

Blah blah blah

\subsubsection{Native parallelisation} \hfill \break

Blah blah blah

%, and discuss some of the remaining theoretical tasks required to make such a goal a reality. 
\fi
\section{Probability Boxes}
\label{sec:pboxes}
